\begin{rSection}{Research Experience}
{\bf Deep Contraction Control of Dynamic Systems} \hfill {\em Sept 2020-June2022}\\
University of California, Irvine, Cooperative Systems Lab\\
{\footnotesize Studying the characteristics of dynamics models to enforce extra criteria on neural networks to learn a more accurate model.}

{\bf Distributed Optimization of Submodular Functions} \hfill {\em Aug 2019-June 2022}\\
University of California, Irvine, Cooperative Systems Lab\\
{\footnotesize Exploring the methods for a multi-agent system to decide on the best local policy without the assist of a central authority.}

{\bf Bayesian Filtering} \hfill {\em Jun 2018-Aug 2019}\\
University of California, Irvine, Cooperative Systems Lab\\
{\footnotesize Using an RFID antenna in conjunction with a Bayesian detection framework to locate an RFID target tag in a monitored area.}

{\bf Persistent Monitoring} \hfill {\em Dec 2017-Aug 2019}\\
University of California, Irvine, Cooperative Systems Lab\\
{\footnotesize Optimal path planning and decision making of a group of agents over a given map to explore and detect possible events in a probabilistic setup.}

{\bf Privacy Preservation of Networked Systems} \hfill {\em Jun 2016-Dec 2017}\\
University of California, Irvine, Cooperative Systems Lab\\
{\footnotesize Designing algorithms to help the nodes in a networked system to preserve their information privacy without a drop in the performance of the network.}

{\bf System Identification and Adaptive Controller Design} \hfill {\em Jan 2015-Jun 2016}\\
Missouri University of Science and Technology, PMC Lab\\
{\footnotesize Developed a C++ program to automatically identify dynamics of a API laser tracker and automatically tune a robust PID controller evading the structural resonance.}

{\bf Star Tracker Prototyping} \hfill {\em Sept 2013-Dec 2014}\\
Sharif University of Technology, Undergraduate Researcher\\
{\footnotesize Designed a star tracker's hardware and star detection algorithm. A working prototype was fabricated using a camera module and a microcontroller.}

\end{rSection}